% ----------------------------------------------------------
%
% log_2024.tex
% This is the main file of LoG 2024 submission
% created by: José G. Quenum
% created on: Aug. 11th 2024
% updated on: 2024
%
% ---------------------------------------------------------

\documentclass{article}
%\usepackage{log_2024}						% for camera-ready version
 \usepackage[review]{log_2024}				% for anonymous submission to proceedings track
% \usepackage[review,eatrack]{log_2024}		% for anonymous submission to extended abstract track
% \usepackage[preprint]{log_2024}			% for preprint version
% \usepackage[eatrack]{log_2024}				% for accepted extended abstracts

\usepackage{booktabs}						% professional-quality tables
\usepackage{multirow}						% tabular cells spanning multiple rows
\usepackage{amsfonts}						% blackboard math symbols
\usepackage{graphicx}						% figures
\usepackage{duckuments}						% sample images
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{latexsym}
\usepackage{amsthm}
\usepackage{enumitem}
\usepackage{color}
\usepackage{soul}
\usepackage{url}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=10pt,font=small,labelfont=bf, labelsep=endash]{caption}
\usepackage{tikz}
\usepackage[linesnumbered,algoruled,vlined,boxed,commentsnumbered]{algorithm2e}
\usepackage[]{algpseudocode}
\usepackage{listings}
\usepackage{complexity}
\usepackage{siunitx}
\usepackage{newtxmath}
\usepackage{textcomp}
\usepackage{csquotes}
\usepackage{subcaption}
\usepackage{tasks}
\usepackage{todonotes}
\usepackage[numbers,compress,sort]{natbib}
\usepackage{subcaption}

% If you want to use bibLaTeX, uncomment below:
% \usepackage[
%      backend=biber,
%      style=numeric-comp,
%      backref=true,
%      natbib=true]{biblatex}
% \addbibresource{reference.bib}
\usepackage[acronym]{glossaries}
%\crefalias{AlgoLine}{line}%

%\usepackage{cleveref}

\newlength{\commentWidth}
\setlength{\commentWidth}{4cm}
\newcommand{\atcp}[1]{\tcp*[r]{\makebox[\commentWidth]{#1\hfill}}}

% If you want to use natbib:
%\usepackage[numbers,compress,sort]{natbib}	% for numerical citations
% \usepackage[sort,round]{natbib}			% for textual citations


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% Define any theorem-like environments you require here.

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{fact}[theorem]{Fact}
%\newtheorem{definition}{Definition}
\newtheorem{example}{Example}
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\crefname{section}{section}{sections}
%\Crefname{section}{Section}{Sections}
%\crefname{subsection}{section}{sections}
%\Crefname{subsection}{Section}{Sections}
%\crefname{figure}{figure}{figures}
%\Crefname{figure}{Figure}{Figures}
%\crefname{table}{table}{tables}
%\Crefname{table}{Table}{Tables}
%\crefname{algocf}{algorithm}{algorithms}
%\Crefname{algocf}{Algorithm}{Algorithms}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\DeclareGraphicsExtensions{.pdf, .png, .jpg}
\graphicspath{{./images/}}
\sloppy

\makeglossaries

\newacronym{gnn}{GNN}{Graph Neural Network}
\newacronym{cnp}{CNP}{card-not-present}
\newacronym{nlp}{NLP}{natural language processing}

\title[Phishing Banking Information]{Client-side Alert on Banking Information Theft}

\author[Quenum and Gamundani]{%
  Jos\'{e} Quenum \and Attlee Gamundani\\
Namibia University of Science and Technology, Windhoek\\
\email{jquenum@nust.na\quad agamundani@nust.na}}

\begin{document}

\maketitle

\begin{abstract}
  This paper proposes an alert mechanism for potential banking information theft on the user side. While much effort has been invested in developing safer E-Commerce and online transactional applications to protect vendors, more needs to be accomplished to protect the clients of such systems against phishing. Generally, they are presented with recommendations and good practices to guard against fraudsters attempting to steal critical banking information from them. We argue that fraudsters use ever-changing social engineering tactics which often render these practices obsolete. This paper proposes a proactive approach to trigger an alert on potential phishing of banking information.  A typical scenario of phishing tactics uses an email to lure the user into clicking on a link with a URL corresponding to a Web interface where the critical information is captured. Our approach analyses the link and look for similar, mainly phonetically-sounding,  domain names. We further compare the web pages and the forms that capture the information. We transform these forms into graphs and compare them using a convolutional graph neural network (GNN). The intuition behind our approach suggests that the co-existence of similar phonetically sounding domains with almost identical web forms raises the probability of some of these domains being \emph{illegitimate}. Thus, we trigger an alert cautioning the user about a potential information theft. Our approach focuses on banking information theft. We present the approach and report on the results of our experiments.
\end{abstract}
